Global adjoint tomography -- Model GLAD-M25 \\ Supplementary Material

### 2020-02-18 response_to_reviewers.tex

\rev{I wonder what window sorting and cleaning entails. How many outliers are eliminated?
}

\response{After plotting traveltime histograms towards the end of the window selection process, we clip the tails of the distribution, eliminating ~$3\sigma$~outliers.
This entails just a handful of ~$3\sigma$~outliers that may contaminate the model update.
}

\rev{They smooth the gradient differently to what they did in their previous 15 iterations. Has this a large effect? Obviously they must have a reason for changing this based on some tests.
}

\response{We did not use multi-scale smoothing to better observe the effect of our new weighting scheme in the inversion. The weighting strategy is discussed in detail in~Ruan et al.~(2019), and includes examples of improved convergence.
One may still use multi-scale smoothing with the new weighting scheme to allow for smaller-scale heterogeneities under densely sampled regions. We have now noted this in the main text. 
}

@@

\rev{Concerning the model evaluation, they refrained from point spread functions. Instead they show detailed misfits and comparisons with other published models.
I can understand that PSFs are computationally expensive (by the way they could reference the authors who suggested them first for FWI), but they are the only objective way to assess resolution.
Comparisons with existing models are not very helpful if these models have been done with different theories, data etc.
I would suggest at least to make a detailed comparison with GLAD-M15. Do we get visually a better resolution by throwing that much more data and GPU time at the problem. I suspect yes, but I still would like to see what improves where. 
}

\response{We provide detailed comparisons between M15 and M25 in Tables~1 and~2, as well as in all the traveltime and amplitude histograms.
In the revised manuscript we have also added a couple of new figures directly comparing M15 and M25, thereby highlighting distinct new features in M25. In addition we have performed six PSF tests in the upper and the lower mantle which can be found in the main text and in the supplementary material.}

@@

\rev{The authors mention that checkerboards are expensive. One could also mention that in fact they are useless for assessing resolution.
}

\response{Indeed. See our earlier discussion. We also added this in the main text.}

@@

\rev{In that respect, I find the plume pictures for instance over-interpreted. What tells us that red in the upper mantle means the same as red at the CMB.
If they are confident that it means the same, they can say, for instance, the Iceland plume rises from the CMB, if not, it will be a different story.
The same holds for slabs. I suggest to be a bit more careful than just falling in the old habit that red is hot and blue is cold. The deviations are now so large that these analogies become misleading.
}

\response{We have modified the language.\cyan{??}}

\rev{They don't mention anisotropy, but clearly invert for TI as claimed in the technical section. Do they see any evidence of anisotropy in the lower mantle for instance?
}

\response{As in M15, transverse isotropy in M25 is confined to the upper mantle, because it is mainly constrained by surface waves. Since the misfit reductions in all categories are consistent with each other we have not observed effects of anisotropy in the lower mantle yet.}

@@

We naively assumed that it was obvious from the GLAD-M15 GJI article and the histograms and comparisons with other models in this manuscript.
However, based on the comments of all the reviewers we now directly compare GLAD-M15 and GLAD-M25 in the revised manuscript,
thereby highlighting visual differences between the models, in addition to the the tables with variance reductions and traveltime and amplitude anomaly histograms.

There is still a vast amount of information to be explained in seismograms at the global scale, which requires more iterations and, probably, a more complete parameterization.
However, the reviewer is missing the main point --- or, more likely, we did not explain it well --- which is that we decided to publish GLAD-M25 because its resolution (scale-length of heterogeneities) has become comparable to the current resolution of global models from various other groups.
Thus we did not arbitrarily decide to publish this model,
and we certainly do not advocate publishing every iteration as a new model.
%We now highlight it in the manuscript that the vast amount of remaining data in the seismograms should continue changing the models which also points out the necessity of our non-linear iterative inversions.

Finally, resolution and uncertainty quantification remain a challenge in FWI,
both in exploration and earthquake seismology.
In lieu of such tools,
as in numerous other studies,
we used traveltime histograms and a held-out dataset to assess performance of our model (thus, it is not a fair comment to say that ``even the slightest effort to assess the resolution of the model" is absent in the original submission).
In the original submission, we did not perform PSF tests, because these are rather limited in value, especially in view of the fact that they only tell you something about one ``point'' in the model for the set up of a particular iteration.
Therefore, a PSF does not say much about uncertainty, but gives an idea of resolution.
Nevertheless,
as mentioned earlier,
the updated manuscript now contains four PSF tests,
and the SOM contains two more,
including model parameter tradeoff.}

@@

\rev{(1) By far my biggest concern is the lack of true scientific innovation. While the authors do mention some recent technological improvements (e.g., the storage algorithm for anelastic kernels and the ASDF data format), all of them have been published before, and are therefore not new. Apart from adding more events and going to slightly higher frequencies, this work is very similar to the previously published work by Bozdag et al. (2016). Also, the final model does not reveal anything about the structure of the Earth that was not known before.
}

\response{The main technical improvement is workflow management. We do not understand what the reviewer considers ``true scientific innovation", but we take it as an unfortunate, insulting comment. Technical developments are not scientific innovations by themselves, but facilitate them. (For example, this paper would have been impossible without porting our solvers to GPUs.) For this reason we emphasize the technical advances which now enable us to process data from 1,480 events, and more! We understand the concern that the structure of the original paper was close to that of the GLAD-M15 paper,
and we have revised the structure and added a section with direct comparisons between M15 and M25 to highlight their  differences.
}

@@

First of all, if one runs out of computational resources needed to check the quality of a model, it simply means that the inversion has been poorly planned! I am sure the authors know the number of node hours per forward run very well. It is therefore simply a matter of choosing a minimum period that leaves enough resources to run a reasonable model assessment. Simply saying that you better like to use the INCITE resources to just produce a colorful model, is a miserable excuse that I find completely unacceptable.

Second, it is not clear what to learn from 2 point-spread functions (apart from the fact that they were computed for different data). As the authors demonstrate in section 10 of their manuscript (interpretation and comparison), there are many more than 2 interesting points inside the Earth.

Third, the authors dedicate 13 pages (!!!) to the comparison of their new model to the previous and to other models. However, without any quantitative information on how much the new model has improved, this seems to be a rather meaningless exercise.
}

\response{We welcome scientific criticisms, however it is not acceptable that the reviewer completely ignores the fact that they are targeting a student,
%they is gender neutral
who is the first author of this manuscript.
We believe the reviewer is fully aware of the pitfalls of resolution analysis and uncertainty quantification in all tomographic inversions, unless a Bayesian approach is used, which is not even possible for classical global tomographic inversions.
The reason we did not perform PSF tests was not because we ran out of core-hours but chose not to use them for this purpose,
because a few PSF tests do not say much about global resolution.
%The reason we mentioned the cost of PSF tests in the original manuscript was rather to make the point that despite the cost we will not get the full resolution. Otherwise, the core hours have never been an issue for our INCITE allocations but the ability to handle large data sets in FWI while carefully investigating the model evolution is the main challenge. 
Nevertheless, we added six PSF tests in the revised manuscript in addition to our existing quantitative comparisons of traveltime and amplitude misfits.
}

@@

\response{
Based on our estimation, there are about 6,000~events in the global CMT catalog suitable for global FWI.
So to say that at 1,480 events our dataset is ``not overwhelming'' seems rather harsh,
even more so if one considers that the only other global FWI efforts,
the Bozdag et al. (2016) and French \& Romanowicz (2015),
used just a few hundred events.
We also emphasize that the information going into the model,
as illustrated in the measurement window density maps shown in Figs.~2--4, is large.
This is another strength of our technique.
}

\rev{(4) I am also quite concerned about the writing and presentation style. The sections on supercomputing sound pretentious, which is a high risk for the authors, given that their model does not tell us many new things about the internal structure of the Earth. 
}

\response{
We did not intend for the sections on supercomputing to sound grandiose; we were merely attempting to convey the computational challenges and how these were overcome.
Much of this work was accomplished by the student first-author of the paper, and we were trying to highlight these rather nontrivial accomplishments.
Nevertheless, also in view of comments by other reviewers and the editor, we have toned down the language in the revised manuscript.

The statement ``their model does not tell us many new things about the internal structure of the Earth'' is again unnecessarily harsh and uncalled for. We already emphasize the advantages of our models, as we believe the reviewer knows well. 
For example,
this is one of the few tomographic studies to constrain shear and compressional wavespeeds together in the same frequency band.
Thus, our Vp/Vs ratios certainly add scientific value.
We also invert body and surface waves simultaneously, which is important for constraining upper mantle structure.
Additionally, we make no crustal corrections, 
which too should lead to better constrained images of the deeper Earth.
Finally, in newly added figures visually comparing M15 and M25 numerous new features emerge,
such as several hotspots in the Indian Ocean, etc. 
}

@@

\rev{I must admit that I am disappointed by the model evaluation in Section 10. The comparison with maps and cross-sections from other tomographic models is somewhat superficial and not as persuasive as the earlier sections of the paper.
}

\response{We have removed all the regional and full global comparisons, leaving just the plumes and slab figures, while adding a discussion of differences between M15 and M25, as requested by other reviewers.}

\rev{The manuscript is in decent shape but the writing is somewhat rushed after page 20 or so. The senior authors should polish the text and remove paragraphs, primarily in early sections, on topics that have been covered by Bozdag et al.
The authors don't do the point-spread function analysis so subsection 9.1 can be eliminated. I have annotated the PDF copy to suggest edits and to point out fuzzy wording.
}

\response{We have further polished the writing later in the manuscript
Thanks for the annotated manuscript! We have accommodated most comments and suggestions.
Based on suggestions by the other reviewers,
we added six PSF tests to the manuscript and the supplementary material.}

@@

\rev{The GLAD-M tomography stands out from the other approaches by casting the inverse without compromising the physics of wave propagation. Consequently, the workflow is laborious and iterations are slow. Ten iterations for a moderate data set (compared to the S40RTS data set, for example), took more than two years. Sections 1--9 indicate that the authors are convinced about the value of their approach but the discussion onward from Section 10 is qualitative and not serving the authors' case.
I worry that readers might wonder whether M25 is a significant step forward from M15 and whether the tremendous engineering and use of computer power justifies the (re)discovery of velocity anomalies that do not appear to change our understanding of mantle structure and dynamics.
}

\response{We have modified the manuscript substantially, as discussed previously. We focus more concretely on differences between M15 and M25 to better highlight the power of 10 additional iterations with $>1,000$ events.  
Unfortunately,
comparisons with other models will always be rather qualitative, because we have no way of using such models in 3D wave simulations, mainly because 3D mantle models are difficult to combine with 3D crustal models. Underneath the oceans there tends to be a `gap' between the mantle model and the crust, whereas underneath the continents there tends to be a region of overlap, and this make `gluing' the two together challenging.}

@@

\rev{2. Along the same lines, do the sensitivity kernels for body waves through the deep mantle change from iteration 0 to 25? Always or only when, for example, when they skirt the LLSVP? Would it be sensible to recalculate the high-frequency body-wave kernels only every 5th or 10th iteration to safe computational time? Are there good reasons not to do this?
}

\response{See our response to the previous comment. We do not calculate individual sensitivity kernels a la Dahlen \& Nolet.
%\fromebru{I think we can put such a figure as well (I mean in the response, not sure needed for the paper but may go into SOM as well). The kernels must definitely change for paths across the plumes. Also we may be able to give what I encountered in GLAD-M15 before taking full attenuation into account in adjoint simulations as an evidence that we need to compute exact kernels to further decrease the misfit and improve the model}
%\toebru{Going back to Carl and Qinya's papers, there are lots of such examples in the literature. There is no need to belabor this.}
}

\rev{3. I would like to see examples of recorded and synthetic data at long (T > 250 s), and short (T < 10 s) periods to illustrate that M25 is (close to) reproducing waveform segments and data types not yet selected by FLEXWIN. How good is the fit to waveform segments (e.g., ScS) and data types (e.g., normal mode splitting) not included in the inversion?
}

\response{Calculating synthetics at periods less than 17 s is a very expensive proposition! Going to 9~s involves a 16X increase in the computational cost. The long period corner of the period band is set by the Cowling approximation,
which limits simulations to periods up to $\sim250--300$~s.
}

@@

\rev{4. Source finiteness is already important. A MW7.2 earthquake is assumed to have a duration of 21 seconds (an empirically determined value in the CMT catalog) comparable to the shortest periods used here. What is the effect on the traveltime measurement if the duration is overestimated by 5 or 10 seconds (deep earthquakes tend be more compact)? When higher frequencies are incorporated, do the authors plan to invert for source durations or can they rely on standard catalogs of source time functions (e.g., SCARDEC)?
}

\response{Low pass filtering at 17~s largely eliminates sensitivity to shorter half durations. 
In addition, when the waveform difference caused by the source time function is too large, it will be rejected by our data screening process. Going forward we are planning to do our own CMT inversions in M25, but including an STF estimation.
}

@@

\rev{5. As the authors plan to include attenuation in the parameterization, will this be a new 1-D profile for Q or a fully 3-D structure? How might this affect the inversion for dVs (and dVp)? For example, assuming that dVs and dQ-1 are related linearly ---- take Colleen Dalton's model for a first-order scaling between dVs and dQ-1 ---- how would this change the traveltime fits? How should dVs and dQ-1 be parameterized (and regularized) to assure that the inversion converges to sensible models for both parameters?
}

\response{We are planning a fully 3D Q inversion. This will be a ``proper'' Q inversion,
where there full effects of attenuation, i.e., physical dispersion and dissipation, will be taken into account. We have some experience with such inversions in Europe (Zhu et al., 2013), and for problems in exploration seismology. We have also started experimenting at the global scale. The reviewer is right that the Q model will directly affect the traveltimes;
all tomographic inversions are affected by this.
}

@@

\rev{h) Page 9. It is not clear to me which part(s) of the seismogram the data categories encompass. Can waveform segments classified as ``17-40 s body waves'' overlap with segments from the ``40-100 s body waves'' group? It would be helpful to show four seismograms for the different frequency bands that indicate where windows are typically chosen.
}

\response{The windows are taken independently of categories, based on the quality of fit. Examples of such windows may be found in Bozdag et al.~(2016).}

\rev{i) Page 10. Was the imbalance in M15 (e.g., thousands of paths between circum-Pacific events and the USArray) the motivation for the source and receiver weights in equations 5 and 6?
}

\response{Yes. M15 tried to compensate for this based on kernel density weighting, but the new approach demonstrably leads to faster and better convergence (see Ruan et al.~2019).}

@@

\rev{j) Figure 6. Both PS and SP can be strong on the vertical and radial components. So, change the label ``PS'' to ``SP+PS''. Why are there few segments close to the PPP arrival (beyond 100 degrees)? Since it is used in the caption, I would use seconds along the y-axis (also in the next two figures).
}

\response{Points taken. PPP is not prominent, and picked rarely by Pyflex with conservative selection criteria to avoid bad-quality windows. It is ongoing research to improve automated phase picking algorithms.}

@@

q) In Figure 18 I suggest to include the model by Krischer et al. (JGR; 2018). Model US22 is perhaps not that useful in the context of this comparison since it is based on a similar modeling approach and data set as M25.

r) Since SL2013NA (a ``ray'' model) doesn't appear too different from M25 it is not clear from the visual comparison) whether modeling improvements (i.e., better theories) matter.
(Note that I suspect they do matter for surface waves because your variance reduction is large for the surface wave data -- see my point 1).

s) The differences among the models at depths larger than 300 km in Figure 18 is striking.
The authors draw the reader's attention to anomalies with well-understood tectonic origins but at face value the images are really very different especially for US22 (and M25) and SL2013NA.
The latter model is based on a large set of overtone surface wave data that should sample the MTZ very well. The misfit reduction obtained for the 40-100 s body + surface waves (presumably waveform segments after SS and before the fundamental mode surface wave) is relatively poor, so perhaps the MTZ in M25 is still poorly resolved (or S362 was an excellent model to begin with).
At any rate, this need further discussion. Transition zone resolution is still a sticky point and is important for understand convective flow.

\response{Due to our cross-correlation measurements higher-modes may well be underrepresented in the current inversions. We are working on other misfit functions to effectively incorporate smaller-amplitude signals (e.g., Yuan et al. 2020) together with better window-selection strategies.}

### 2020-02-18 supplementary_material.tex
Updates from Overleaf

To update the source parameters (six moment tensor components, latitude, longitude and depth) using the starting model to compute the Green's functions for each source parameter,
we used the CMT inversion algorithm of \cite{liu2004spectral}.
This algorithm combines a normalized waveform difference misfit with an envelope difference misfit.
Specifically, the algorithm minimizes the misfit function
\begin{equation}
   \begin{split}
      \Phi =  \sum\limits_{c=1}^{C} \omega_c \sum\limits_{r=1}^{R_c} \omega_{cr}
       \sum\limits_{w=1}^{W_{cr}} \omega_{crw}\,
          & \left\{ \lambda\, \frac
              { \int \big[ d_w(t) - s_w(t - \Delta t) \big]^2 \mathrm{d}t}
              {\int \big[ d_w(t) \big]^2  \mathrm{d}t} \right.
       \\ & \quad \left. \mbox{} + (1 - \lambda)\, \frac
              {\int \big[ e(d_w(t)) - e(s_w(t - \Delta t)) \big]^2 \mathrm{d}t}
              {\int \big[ e(d_w(t)) \big]^2\mathrm{d}t} \right\}
              \quad ,
   \end{split}
\end{equation}
where~$d_w(t)$ denotes data in time window~$w$\,,
and~$s_w(t - \Delta t)$ the corresponding synthetic for model~GLAD-M15.
We allow the synthetics to shift relative to the data by an amount~$\Delta t$
--- effectively a station correction --- determined by cross correlation. We do not invert for the origin times as we minimize the phase misfit due to the station correction which helps to reduce the nonlinearity of the problem. As we describe later, we take into account the uncertainty in origin times, as well as the scalar moment, by performing an additional grid search at every iteration.
The envelope function is denoted by~$e(\,\cdot\,)$\,,
and the parameter~$\lambda$ determines the balance between fitting waveforms versus fitting envelopes.
The number of measurement categories is denoted by~$C$\,.
Following~\cite{ekstrom2012global},
seismograms were filtered between 40~s and 100~s
to select three-component body-wave windows,
and between 60~s and 100~s to select three-component
surface-wave windows,
resulting in six measurement categories, $c=1,\ldots,C$\,.
To balance their contributions,
each category is weighted by the reciprocal of the number of measurements in that
category, $\omega_c$\,.
The number of windows for a given receiver~$r$ in a given measurement category~$c$ is~$W_{cr}$\,.
Each such window is weighted equally, i.e.,~$\omega_{crw}=1$\,.
The number of receivers that records data in category~$c$ is denoted by~$R_c$\,.
As shown in Fig.~\ref{fig:source_correction}b,
the receivers are unevenly distributed across the globe,
with several dense arrays in the northern hemisphere and poor coverage in the southern hemisphere.
To balance the coverage,
following a strategy articulated by~\cite{Ruanetal2018},
we assign receiver weights~$\omega_{cr}$ based on the expression
\begin{equation}
\omega_{cr}^{-1} = N_c\,\sum_{r'=1}^{R_c} \exp\left[\mbox{}-\left(\frac{\Delta_{rr'}}{\Delta_c}\right)^2\right]
\quad ,
\label{eq:spatial_weights}
\end{equation}
where~$N_c$ is a normalization factor for category~$c$,
and where~$\Delta_{rr'}$ denotes the angular distance between receivers~$r$ and~$r'$\,.
The reference angular distance~$\Delta_c$ for each category~$c$ needs to be chosen such that the condition 
number of the diagonal weighting matrix defined by Eqn.~(\ref{eq:spatial_weights}) is not too large.
The calculation of the weights may be abstracted as: given a distribution of
points on the unit sphere, determine a spatial weighting associated with each point.

@@

Most earthquakes, specifically the oceanic ridge events, are shallower after inversion
(Fig.~\ref{fig:source_correction}c),
consistent with our previous experiences~\citep[e.g.,][]{zhu2015seismic,chen2015multiparameter,bozdaug2016global} and with experiments by~\cite{hjorleifsdottir2010effects}. This is partly because the minimum depth of CMT events are fixed to $\sim12$~km as the sensitivity of source parameters significantly decreases closer to the free surface. 
We observed an average depth change of~$-2.62\pm2.49$~km relative to the global CMT solutions,
an average scalar moment change of~$5.31\pm3.91$\%,
and an average centroid time shift of~$-0.60\pm1.17$~s.
These are relatively minor corrections mainly due to our choice of being conservative in source corrections to avoid nonlinearities and our not-so-detailed crustal model (an updated version of CRUST2.0 through the 15 iterations performed for GLAD-M15), especially in view of the significant expense of the source inversions.
For this reason, when we added another 440 earthquakes during iteration~22,
thereby bringing the total to~1,480 events,
we only performed a grid search to calibrate the centroid times and scalar moments.

@@

This section summarizes the complete Point Spread Function (PSF) tests conducted as part of this study, including the tradeoff between parameters.
Figs.~\ref{fig:psf_yellowstone}--\ref{fig:psf_su} show the results of PSF tests underneath Yellowstone, Easter Island, Afar, and Sumatra.
Each figure shows the original Gaussian perturbation in vertically polarized shear wavespeed, $\mathsf{\Delta}\mathsf{m}$\,, in map view and cross section, as well as the action of the Hessian on this model perturbation, $\mathsf{H}\mathsf{\Delta}\mathsf{m}$\,.
\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/yellowstone.pdf}
  \caption{\small{PSF test for Yellowstone.
  A 100~km diameter negative Gaussian anomaly is placed at a depth of 300~km beneath Yellowstone.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_yellowstone}
\end{figure}

@@

At a depth of 100~km, we observe that the edges of the craton are sharper in
GLAD-M25 than in the other two global models,
and quite similar in shape and sharpness to the two regional models.
We can see impressions of the Snake River Plain (with Yellowstone)
and the Raton hotspot, which also have slow expressions at depths of 200~km.
The core of the craton exhibits fast wavespeeds at depths reaching 300~km Northwest of
Hudson Bay.
In the regional models the craton has basically faded away at these depths.
The Wyoming and Medicine Hat Blocks show a very strong and thick lithospheric
root from shallow depths to $\sim$400~km, similar to US22 but
difficult to discern in SL2013NA.
Similar observations can be made for the Yavapai and
Mazatzal Blocks, which define the southern boundary of the large craton
~\citep{schaeffer2014imaging}.

In the 200--400~km depth range, we observe a low wavespeed anomaly beneath the Arctic
and s high wavespeed
anomaly within the Gulf of Mexico, which coincides spatially with the deepest
bathymetry and corresponds to a portion of ancient oceanic
lithosphere~\citep{muller2008, schaeffer2014imaging}.
A remnant of the Juan de Fuca plate,
with a high wavespeed footprint, is visible at depths of 300~km and 400~km,
where SL2013NA shows a much stronger anomaly.

>>>>

To update the source parameters (six moment tensor components, latitude, longitude and depth) using the starting model to compute the Green's functions for each source parameter,
we used the CMT inversion algorithm of \cite{liu2004spectral}.
This algorithm combines a normalized waveform difference misfit with an envelope difference misfit.
Specifically, the algorithm minimizes the misfit function
\begin{equation}
   \begin{split}
      \Phi =  \sum\limits_{c=1}^{C} \omega_c \sum\limits_{r=1}^{R_c} \omega_{cr}
       \sum\limits_{w=1}^{W_{cr}} \omega_{crw}\,
          & \left\{ \lambda\, \frac
              { \int \big[ d_w(t) - s_w(t - \Delta t) \big]^2 \mathrm{d}t}
              {\int \big[ d_w(t) \big]^2  \mathrm{d}t} \right.
       \\ & \quad \left. \mbox{} + (1 - \lambda)\, \frac
              {\int \big[ e(d_w(t)) - e(s_w(t - \Delta t)) \big]^2 \mathrm{d}t}
              {\int \big[ e(d_w(t)) \big]^2\mathrm{d}t} \right\}
              \quad ,
   \end{split}
\end{equation}
where~$d_w(t)$ denotes data in time window~$w$\,,
and~$s_w(t - \Delta t)$ the corresponding synthetic for model~GLAD-M15.
We allow the synthetics to shift relative to the data by an amount~$\Delta t$
--- effectively a station correction --- determined by cross correlation. We do not invert for the origin times as we minimize the phase misfit due to the station correction which helps to reduce the nonlinearity of the problem. As we describe later, we take into account the uncertainty in origin times, as well as the scalar moment, by performing an additional grid search at every iteration.
The envelope function is denoted by~$e(\,\cdot\,)$\,,
and the parameter~$\lambda$ determines the balance between fitting waveforms versus fitting envelopes.
The number of measurement categories is denoted by~$C$\,.
Following~\cite{ekstrom2012global},
seismograms were filtered between 50~s and 100~s
to select three-component body-wave windows,
and between 60~s and 100~s to select three-component
surface-wave windows,
resulting in six measurement categories, $c=1,\ldots,C$\,.
To balance their contributions,
each category is weighted by the reciprocal of the number of measurements in that
category, $\omega_c$\,.
The number of windows for a given receiver~$r$ in a given measurement category~$c$ is~$W_{cr}$\,.
Each such window is weighted equally, i.e.,~$\omega_{crw}=1$\,.
The number of receivers that records data in category~$c$ is denoted by~$R_c$\,.
As shown in Fig.~\ref{fig:source_correction}b,
the receivers are unevenly distributed across the globe,
with several dense arrays in the northern hemisphere and poor coverage in the southern hemisphere.
To balance the coverage,
following a strategy articulated by~\cite{Ruanetal2018},
we assign receiver weights~$\omega_{cr}$ based on the expression
\begin{equation}
\omega_{cr}^{-1} = N_c\,\sum_{r'=1}^{R_c} \exp\left[\mbox{}-\left(\frac{\Delta_{rr'}}{\Delta_c}\right)^2\right]
\quad ,
\label{eq:spatial_weights}
\end{equation}
where~$N_c$ is a normalization factor for category~$c$,
and where~$\Delta_{rr'}$ denotes the angular distance between receivers~$r$ and~$r'$\,.
The reference angular distance~$\Delta_c$ for each category~$c$ needs to be chosen such that the condition 
number of the diagonal weighting matrix defined by Eqn.~(\ref{eq:spatial_weights}) is not too large.
The calculation of the weights may be abstracted as: given a distribution of
points on the unit sphere, determine a spatial weighting associated with each point.

@@

Most earthquakes, specifically the oceanic ridge events, are shallower after inversion
(Fig.~\ref{fig:source_correction}c),
consistent with our previous experiences~\citep[e.g.,][]{zhu2015seismic,chen2015multiparameter,bozdaug2016global} and with experiments by~\cite{hjorleifsdottir2010effects}. This is partly because the minimum depth of CMT events are fixed to $\sim12$~km as the sensitivity of source parameters significantly decreases closer to the free surface. 
We observed an average depth change of~$-2.62\pm2.49$~km relative to the global CMT solutions,
an average scalar moment change of~$5.31\pm3.91$\%,
and an average centroid time shift of~$-0.60\pm1.17$~s.
These are relatively minor corrections mainly due to our choice of being conservative in source inversions to avoid nonlinearities and our not-so-detailed crustal model (an updated version of CRUST2.0 through the 15 iterations performed for GLAD-M15), especially in view of the significant expense of the source inversions.
For this reason, when we added another 440 earthquakes during iteration~22,
thereby bringing the total to~1,480 events,
we only performed a grid search to calibrate the centroid times and scalar moments.

@@

This section summarizes the complete Point Spread Function (PSF) tests conducted as part of this study, including the tradeoff between parameters.
Figs.~\ref{fig:psf_yellowstone}--\ref{fig:psf_su} show the results of PSF tests underneath Yellowstone, Easter Island, Afar, and Sumatra.
Each figure shows the original Gaussian perturbation in vertically polarized shear wavespeed, $\mathsf{\Delta}\mathsf{m}$\,, in map view and cross section, as well as the action of the Hessian on this model perturbation, $\mathsf{H}\mathsf{\Delta}\mathsf{m}$\,.

We used different sizes of Gaussian perturbations in the PSF tests, from 160~to~400 km diameters depending on the kernel coverage of the selected regions both in the upper and lower mantles. Although we observe some smearing effects the Gaussian anomalies are overall well-recovered. As expected PSF tests are most successful in North America, where we have the best coverage, thanks to USArray. However, it is also encouraging to see good recovery in the lower mantle to assess the resolution of lower-mantle plumes. We observe limited smearing onto other parameters where we observe a slight tradeoff in radial anisotropy in the upper mantle for the tests performed underneath North America.

\begin{figure}
  \centering
  \includegraphics[width=0.65\textwidth]{figures/psf/yellowstone.pdf}
  \caption{\small{PSF test for Yellowstone.
  A 100~km diameter negative Gaussian anomaly is placed at a depth of 300~km beneath Yellowstone.
  Top row: Map view (Left) and cross section (Right) through a Gaussian perturbation in~$\beta_\mathrm{V}$.
  Second row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{V}$.
  Third row: Map view (Left) and cross section (Right) through the recovered perturbation in~$\beta_\mathrm{H}$.
  Bottom row: Map view (Left) and cross section (Right) through the recovered perturbation in the bulk sound speed~$c$. We conclude that there is little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and ~$c$.
  }}
  \label{fig:psf_yellowstone}
\end{figure}

@@

At a depth of 100~km, we observe that the edges of the craton are sharper in
GLAD-M25 than in the other two global models,
and quite similar in shape and sharpness to the two regional models.
We can see impressions of the Snake River Plain (with Yellowstone)
and the Raton hotspot, which also have slow expressions at depths of 200~km. The PSF test we performed in this region~(Fig.~\ref{fig:psf_yellowstone})~gives us confidence on the resolution of the observed anomalies. It is also promising to see the convergence of our global model to the resolution of continental-scale studies specifically in densely covered regions.
The core of the craton exhibits fast wavespeeds at depths reaching 300~km Northwest of
Hudson Bay.
In the regional models the craton has basically faded away at these depths.
The Wyoming and Medicine Hat Blocks show a very strong and thick lithospheric
root from shallow depths to $\sim$400~km, similar to US22 but
difficult to discern in SL2013NA which may be due to similar theory and measurement techniques were used in the construction of GLAD-M25 and US22.
Similar observations can be made for the Yavapai and
Mazatzal Blocks, which define the southern boundary of the large craton
~\citep{schaeffer2014imaging}.

In the 200--400~km depth range, we observe a low wavespeed anomaly beneath the Arctic
and high shear-wavespeed
anomaly within the Gulf of Mexico, which coincides spatially with the deepest
bathymetry and corresponds to a portion of ancient oceanic
lithosphere~\citep{muller2008, schaeffer2014imaging}.
A remnant of the Juan de Fuca plate,
with a high wavespeed footprint, is visible at depths of 300~km and 400~km,
where SL2013NA shows a much stronger anomaly.
